### 2021-01-20 README.Rmd
rcpp speed up, clean up of arrangeGrob + grid.arrange, and additional comment in readme

    c. Finally, we've also leveraged ideas from [R-devel: on avoiding problems with `:::`](https://stat.ethz.ch/pipermail/r-devel/2013-August/067210.html) in `R/aaa.R` to overcome messages from CRAN relative to this hack (using `:::`). For some reason - when documenting for `pkgdown` website, we need to do `library(ggtern); EpiCompare:::update_approved_layers()`
3. `geom_prediction_band` required not just `compute_group` but `compute_layer` - there is very little documentation on how to approach this correctly. Basically - there are problems when the `compute_group` wants to make multiple `pieces`/`groups` - and it is similar to the problem that if you do something like `aes(color = var1, group = var2)` you may actually want to do `aes(color = var1, group = paste(var1, var2))`, if there are the same `var2` values across different `var1` value, but should not necessarily be grouped together.
4. Now that `R` has come out with version >= 4.0.0, we now need to call `.S3method("method", "class")` to define the connection for `S3` methods (e.g. `method.class` function), which we have for the `contained` function. 
5. **Do two wrongs make a right?** As of 9/23 `ggtern` had an [issue](https://bitbucket.org/nicholasehamilton/ggtern/issues/13/ggtern-breaks-ggplots-plot) that it messed with `ggplot2`'s legends when loaded (it over-wrote the `print.ggplot` and other functions). We've over-written `ggtern`'s `print.ggplot` to correct this problem when not producing ternary plots (code in `aaa.R`). 
6. Useful Rstudio shortcuts for `Roxygen2`: (a) create `Roxygen2` comments template with `option` + `command` + `shift` + `R` (b) In `Roxygen2` comments do `control` + `shift` + `/` to format relative to 80 char limit.
7. [stack overflow](https://stackoverflow.com/questions/11285496/r-cmd-check-warning-functions-methods-with-usage-in-documentation-object-bu) post on how to pass `check` for `rownames<-.tidy_dist_mat`.
8. Transferring from Travis CI to github actions. We only use a single workflow file (although we use code ideas found in: [check-standard/`usethis::use_github_action_check_standard()`](https://github.com/r-lib/actions/blob/master/examples/check-standard.yaml)), [test-coverage/`usethis::use_github_action("test-coverage")`](https://github.com/r-lib/actions/blob/master/examples/test-coverage.yaml). In our `.github/workflows/R-CMD-check-coverage.yaml` you'll find **a** (potentially not optional) approach to preform our complex checking approach (which tries to copy the ideas in our [old travis file](https://github.com/skgallagher/EpiCompare/blob/e1298f799d9248bb330885ba5e7b0fa17ea2c83e/.travis.yml)). The github action easily creates a *larger* matrix that allows us to run on all standard OS, R versions and our "tidyr-current" vs "tidyr-old" split. Our approach with 1 github action `yaml` file makes us only look at 8 matrix options - it's possible that, in the future, we'll go back to 3 files. We currently compile our `pkgdown` site on our own computers and then push - and will continue to do so due to complications with `reticulate` and `python` packages on the virtual machines in github actions.

>>>>

    c. Finally, we've also leveraged ideas from [R-devel: on avoiding problems with `:::`](https://stat.ethz.ch/pipermail/r-devel/2013-August/067210.html) in `R/aaa.R` to overcome messages from CRAN relative to this hack (using `:::`). For some reason - when documenting for `pkgdown` website, we need to do `library(ggtern); EpiCompare:::update_approved_layers()`
3. `geom_prediction_band` required not just `compute_group` but `compute_layer` - there is very little documentation on how to approach this correctly. Basically - there are problems when the `compute_group` wants to make multiple `pieces`/`groups` - and it is similar to the problem that if you do something like `aes(color = var1, group = var2)` you may actually want to do `aes(color = var1, group = paste(var1, var2))`, if there are the same `var2` values across different `var1` value, but should not necessarily be grouped together.
4. Now that `R` has come out with version >= 4.0.0, we now need to call `.S3method("method", "class")` to define the connection for `S3` methods (e.g. `method.class` function), which we have for the `contained` function. 
5. **Do two wrongs make a right?** As of 9/23 `ggtern` had an [issue](https://bitbucket.org/nicholasehamilton/ggtern/issues/13/ggtern-breaks-ggplots-plot) that it messed with `ggplot2`'s legends when loaded (it over-wrote the `print.ggplot` and other functions). We've over-written `ggtern`'s `print.ggplot` to correct this problem when not producing ternary plots (code in `aaa.R`). 
6. Useful Rstudio shortcuts for `Roxygen2`: (a) create `Roxygen2` comments template with `option` + `command` + `shift` + `R` (b) In `Roxygen2` comments do `control` + `shift` + `/` to format relative to 80 char limit.
7. [stack overflow](https://stackoverflow.com/questions/11285496/r-cmd-check-warning-functions-methods-with-usage-in-documentation-object-bu) post on how to pass `check` for `rownames<-.tidy_dist_mat`.
8. Transferring from Travis CI to github actions. We only use a single workflow file (although we use code ideas found in: [check-standard/`usethis::use_github_action_check_standard()`](https://github.com/r-lib/actions/blob/master/examples/check-standard.yaml)), [test-coverage/`usethis::use_github_action("test-coverage")`](https://github.com/r-lib/actions/blob/master/examples/test-coverage.yaml). In our `.github/workflows/R-CMD-check-coverage.yaml` you'll find **a** (potentially not optional) approach to preform our complex checking approach (which tries to copy the ideas in our [old travis file](https://github.com/skgallagher/EpiCompare/blob/e1298f799d9248bb330885ba5e7b0fa17ea2c83e/.travis.yml)). The github action easily creates a *larger* matrix that allows us to run on all standard OS, R versions and our "tidyr-current" vs "tidyr-old" split. Our approach with 1 github action `yaml` file makes us only look at 8 matrix options - it's possible that, in the future, we'll go back to 3 files. We currently compile our `pkgdown` site on our own computers and then push - and will continue to do so due to complications with `reticulate` and `python` packages on the virtual machines in github actions.
9. We've speed up some of the interval functions with `Rcpp`. The setup to use this functions was slightly complex, we drafted code using `cppFunction('...')` and then needed to pipe them over to the package setting. Approaches required (1) `usethis::use_rcpp()`, then copying C++ code into `src/code.cpp` (needed to make sure we had [`// [[Rcpp::export]]`](http://adv-r.had.co.nz/Rcpp.html#rcpp-sugar) above each function. For make sure the functions would be compiled and available we needed to update the package documentation with [2 roxygen tags](https://r-pkgs.org/src.html#cpp):

```
#' @useDynLib your-package-name
#' @importFrom Rcpp sourceCpp
```
